% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 

\begin{document} 

\name{ROSS L. ROTHENSTINE\\[12pt]}     % the \\[12pt] adds a blank
				        % line after name      

\address{\bf  PRESENT ADDRESS\\10325 Frazeysburg Rd.\\Dresden, OH 43821\\(740) 586-8749\\www.rossrothenstine.com}
\begin{resume}

\section{JOB OBJECTIVE}          
    A position where my skills as a Software Engineer will be put to use coordinating, building,
    and maintaining correct software.        
 
\section{EDUCATION}          
    University of Akron, Akron, OH  \\        
    Bachelor of Science, Computer Science, Cum Laude, December 2012   \\       
    Concentration in Game Development and Graphics       \\           
    G.P.A. 3.6/4.0          

 
\section{EXPERIENCE}
   \vspace{-0.1in}	
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Software Consultant} \>Case Western Reserve University    \>Spring 2013\\
                             \>Cleveland, OH
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    Coordinated with a project lead to architect plugin using Max/MSP/Jitter. Software 
    disciplines included C++, MSVC11, and Git SCM. References available.
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Software Engineer} \> ETactics, Inc. \> Summer 2011\\
                          \>Stow. OH
   \end{tabbing}\vspace{-20pt}
    Worked in a team environment to maintain an existing Java web application. Tasks included
    fixing bugs, managing evolving software and changing requirements. Tools used include Eclipse,
    CVS SCM, and various inhouse proprietary software.       


\section{COMPUTER SKILLS}
  \vspace{-0.1in}
  \begin{tabbing}
  \hspace{2.3in} \= \kill
  Languages: \>  C++, C\#, C, Java, PHP, Lua, Python \\
  Platforms: \> Ubuntu, Android, Win32 \\
  IDEs: \> MSVC, Eclipse, Netbeans, Sublime Text 2 \\
  MVC Frameworks: \> Symfony2, Kohana \\
  Frameworks: \> Qt5, Qt4.8, QtQuick 2 \\
  Graphics: \> OpenGL, Ogre3D \\
  Game Engines: \> Unreal Development Kit, CryEngine 3
  \end{tabbing}

\section{HONORS AND AWARDS}          
    Cum Laude, University of Akron (2013) \\
    Dean's List, College of Arts and Sciences, University of Akron (2009-2013)         
 
\section{EXTRACURRICULAR ACTIVITIES}          
    Staying fit \\
    Biking \\
    Guitar \\
    Gaming  
 
\end{resume}
\end{document}